\begin{titlepage}
    % different margin so titlepage fits into template
    \newgeometry{left=3.5cm,right=2cm}
    \large
     \begin{center}
      Institut für Maschinelle Sprachverarbeitung\\
      Universität Stuttgart\\
      Pfaffenwaldring 5B\\
      D-70569 Stuttgart\\    
      
      \vspace{2.5cm}
      Master thesis\\
     % \vfill
      {\LARGE \bf \Titel} \\
      \vspace{2cm}
      Isaac Riley\\
         \vfill
      \begin{tabular}[t]{lr}
      Studiengang: & M.Sc. Computational Linguistics \\ % oder: B.Sc. Maschinelle Sprachverarbeitung, M.Sc. Informatik, ...\\
      \\
      \\
      {Prüfer*innen:} & Prof. Dr. Wolfgang Wokurek\\
       & Prof. Dr. Antje Schweitzer\\
      {Betreuer:} & Prof. Dr. Wolfgang Wokurek\\ 
      \\
      \\
      {Beginn der Arbeit:} & 06.04.2021\\
      {Ende der Arbeit:} & 06.10.2021\\
      \end{tabular}
    \end{center}
  \setlength{\hoffset}{0cm}
    \normalsize
  \end{titlepage}
  \newgeometry{left=3cm,right=3cm}
  
  \newpage
  \thispagestyle{empty}
  \begin{otherlanguage}
  {german}
  \noindent\textbf{Erklärung (Statement of Authorship)}\\
  
  
  \noindent Hiermit erkläre ich, dass ich die vorliegende Arbeit selbstständig verfasst habe und dabei keine andere als die angegebene Literatur verwendet habe. Alle Zitate und sinngemäßen Entlehnungen sind als solche unter genauer Angabe der Quelle gekennzeichnet. Die eingereichte Arbeit ist weder vollständig noch in wesentlichen Teilen Gegenstand eines anderen Prüfungsverfahrens gewesen. Sie ist weder vollständig noch in Teilen bereits veröffentlicht. Die beigefügte elektronische Version stimmt mit dem Druckexemplar überein.%% delete the following for theses in German; 
  %% delete or keep for English theses. 
  %% The German version above must be retained 
  %% and signed even if the thesis is written
  %% in another language than German.
  \end{otherlanguage}
  \footnote{Non-binding translation for convenience: This thesis is the result of my own independent work, and any material from work of others which is used either verbatim or indirectly in the text is credited to the author including details about the exact source in the text. This work has not been part of any other previous examination, neither completely nor in parts. It has neither completely nor partially been published before. The submitted electronic version is identical to this print version.}\\[2cm]
  \vspace{2cm}
  (Isaac Riley)
  
  \newpage
  \thispagestyle{empty}
  \noindent \textbf{Acknowledgments}\\
  \noindent I wish to express my thanks to Dr. Wokurek for his mentoring and encouragement. 
  He was incredibly generous with his time, and his advice and willingness to listen 
  to my ideas helped me to keep a level head throughout what was at times a difficult 
  research process. I learned from him more than he may suspect, and I will carry his 
  insights and advice with me long after I have submitted my thesis.
\\~\\
  I am eternally indebted to my wife, Sandra, for her assistance and 
  encouragement. 
  In so many ways, she made this possible.
  To her I owe not only my thesis, but also my sanity.
  %I would like to thank my friends for their feedback and encouragement 
  %throughout the entire process. 
  
  
  \newpage
  {\selectlanguage{english}\tableofcontents}
  \newpage